---
title: "Prototype effects in Exemplar Models"
author: "Your name(s)"
date: "Date of submission"
output: 
  html_document: 
    highlight: tango
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

theme_set(theme_classic(base_size = 16))
```

* * *

Make the prototypes
```{r make_prototypes}
# Make prototype A by setting each cell of a 16x16 grid randomly to be white 
# or black
a <- tibble(row = 1:16, col = 1:16) %>%
  expand(row, col) %>%
  mutate(value =  rbinom(256, 1, .5))

# Pick 7 cells from each row and flip their value (to make prototype B)
different <- a %>%
  group_by(row) %>%
  sample_n(7) %>%
  mutate(value = as.numeric(!value)) %>%
  ungroup()

# Find the cells which will not differ between prototypes
same <- anti_join(a, different, by = c("row", "col"))

# Make prototype B
b <- bind_rows(different, same)
```

Plot the prototypes to see what we got
```{r plot_prototypes, fig.width= 8, fig.height= 4}
prototypes <- a %>%
  mutate(prototype = "a") %>%
  bind_rows(mutate(b, prototype = "b"))

ggplot(prototypes, aes(x = row, y = col, fill = as.factor(value))) + 
  facet_wrap(~ prototype) +
  geom_tile(color = "black") + 
  theme(legend.position = "none", axis.text = element_blank(),
        axis.line = element_blank(), axis.ticks = element_blank(),
        axis.title = element_blank()) + 
  scale_fill_manual(values = c("black", "white")) 
```


Write functions that make close and far examplars as in McLaren et al.
```{r make_exemplar}
close_exemplar <- function(prototype) {
  changed <- different %>%
    sample_n(25) %>%
    select(-value) %>%
    left_join(prototype, by = c("row", "col")) %>%
    mutate(value = as.numeric(!value))
  
  anti_join(prototype, changed, by = c("row", "col")) %>%
    bind_rows(changed) %>%
    mutate(type = "close")
} 

far_exemplar <- function(prototype) {
  changed <- same %>%
    sample_n(25) %>%
    select(-value) %>%
    left_join(prototype, by = c("row", "col")) %>%
    mutate(value = as.numeric(!value))
  
  
  anti_join(prototype, changed, by = c("row", "col")) %>%
    bind_rows(changed) %>%
    mutate(type = "far")
} 
```

Plot a close and far exemplar of A
```{r plot_manips, fig.width= 10, fig.height= 2.5}
a_manips <- prototypes %>%
  rename(type = prototype) %>%
  bind_rows(close_exemplar(a) %>% mutate(type = "close a"),
            far_exemplar(a) %>% mutate(type = "far a")) %>%
  mutate(type = factor(type, levels = c("far a", "a","close a", "b")))

ggplot(a_manips, aes(x = row, y = col, fill = as.factor(value))) + 
  facet_grid(. ~ type) +
  geom_tile(color = "black") + 
  theme(legend.position = "none", axis.text = element_blank(),
        axis.line = element_blank(), axis.ticks = element_blank(),
        axis.title = element_blank()) + 
  scale_fill_manual(values = c("black", "white")) 


```

Simulate training (20 per exemplar type)
```{r simulate_training}
N_TYPE <- 20


```

The General Context Model distance function
```{r d_gcm}
d_gcm <- function(x, y, r = 1) {

}
```

The General Context Model similarity function
```{r s_gcm}
s_gcm <- function(d,  c = .01) {

}
```

Luce Choice axiom. You might find it easier to organize it so that the correct category is always first (but of course you can do this however you prefer).
```{r luce_choice}
luce_choice <- function(s_correct, s_incorrect) {
  
}
```

Compute similarities of all new test items to the exemplars from each category
```{r test_similarities}

```


Compute test behavior. Make sure you do this for both $r = 1$ and $r = 2$
```{r test_choices}

```

Plot the results for the two similarity functions
```{r test_plots}

```

Build a very simple prototype model
```{r prototype_model}

```

Plot the outcomes for $r = 1$ and $r = 2$
```{r prototype_plots}

```
